Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-15 talk/pepm2011/paper.tex
- shorten a bit  - mention size of python interpreter

A further complication is that most interpreters written with PyPy use
heap-allocated frame objects to store local variables. Those severely hinders
the effectiveness of allocation removal, because every time an object is stored
into a local variable, it is stored into the frame-object, which makes it
escape. We implemented a general technique to treat such frames objects in a
special way to solve this problem. This is a common approach in VM
implementations \cite{miranda_context_1999,andreas_gal_trace-based_2009}. The
only novelty in our approach lays in its generality: most other JITs, are just
specifically written for one particular language instead of being generated from
an interpreter.

To evaluate the effectiveness of our allocation removal algorithm, we look at
the effectiveness when used in the tracing JIT of PyPy's Python interpreter. The
benchmarks we used are small-to-medium Python programs, some synthetic
benchmarks, some real applications.\footnote{All the source code of the
benchmarks can be found at \texttt{http://codespeak.net/svn/pypy/benchmarks/}.
There is also a website that monitors PyPy's performance nightly at
\texttt{http://speed.pypy.org/}.}

@@

Furthermore there are the following benchmarks:
\begin{itemize}
    \item \textbf{crypto\_pyaes}: AES implementation.
    \item \textbf{django}: The templating engine of the Django web
    framework\footnote{\texttt{http://www.djangoproject.com/}}.
    \item \textbf{go}: A Monte-Carlo Go
    AI\footnote{\texttt{http://shed-skin.blogspot.com/2009/07/ disco-elegant-python-go-player.html}}.
    \item \textbf{html5lib}: An HTML5 parser.
    \item \textbf{pyflate-fast}: A BZ2 decoder.
    \item \textbf{raytrace-simple}: A ray tracer.
    \item \textbf{richards}: The Richards benchmark.
    \item \textbf{spambayes}: A Bayesian spam filter\footnote{\texttt{http://spambayes.sourceforge.net/}}.
    \item \textbf{telco}: A Python version of the Telco decimal
    benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}},
    using a pure Python decimal floating point implementation.
    \item \textbf{twisted\_names}: A DNS server benchmark using the Twisted networking
    framework\footnote{\texttt{http://twistedmatrix.com/}}.
\end{itemize}

>>>>

A further complication is that most interpreters written with PyPy use
heap-allocated frame objects to store local variables. Those severely hinder
the effectiveness of allocation removal, because every time an object is stored
into a local variable, it is stored into the frame-object, which makes it
escape. We implemented a technique to treat such frames objects in a
special way to solve this problem. This is a common approach in VM
implementations \cite{miranda_context_1999,andreas_gal_trace-based_2009}, the
novelty of our approach is that we generalized it enough to be usable for
different interpreter.

To evaluate our allocation removal algorithm, we look at the effectiveness when
used in the generated tracing JIT of PyPy's Python interpreter. This interpreter
is a full implementation of Python 2.5 language semantics and is about 30'000
lines of code.

The
benchmarks we used are small-to-medium Python programs, some synthetic
benchmarks, some real applications.\footnote{All the source code of the
benchmarks can be found at \texttt{http://codespeak.net/svn/pypy/benchmarks/}.
There is also a website that monitors PyPy's performance nightly at
\texttt{http://speed.pypy.org/}.}

@@

Furthermore there are the following benchmarks:
\begin{itemize}
    \item \textbf{crypto\_pyaes}: An AES implementation.
    \item \textbf{django}: The templating engine of the Django web
    framework\footnote{\texttt{http://www.djangoproject.com/}}.
    \item \textbf{go}: A Monte-Carlo Go
    AI\footnote{\texttt{http://shed-skin.blogspot.com/2009/07/ disco-elegant-python-go-player.html}}.
    \item \textbf{html5lib}: An HTML5 parser.
    \item \textbf{pyflate-fast}: A BZ2 decoder.
    \item \textbf{raytrace-simple}: A ray tracer.
    \item \textbf{richards}: The Richards benchmark.
    \item \textbf{spambayes}: A Bayesian spam filter\footnote{\texttt{http://spambayes.sourceforge.net/}}.
    \item \textbf{telco}: A Python version of the Telco decimal
    benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}},
    using a pure Python decimal floating point implementation.
    \item \textbf{twisted\_names}: A DNS server benchmark using the Twisted networking
    framework\footnote{\texttt{http://twistedmatrix.com/}}.
\end{itemize}
